### 2015-03-24 src/paper4/p4_discussion.tex
Processed Luc and Pieters comments on Intro, P3 and P4
Updated paper 4

% Relation to previous work / Should rewrite this paragraph!
In our previous study, we demonstrated that oculomotor signals play a substantial role in the perception of self-motion, even in the absence of optic flow or any other visual stimulation \cite{clemens2015a}. Although the vestibular system provided the most significant contribution, oculomotor signals were shown to account for about 20\% of the overall percept. Because these experiments were performed with a single fixation depth, it was not clear whether the brain weighted the oculomotor signal in a depth-dependent manner when using it as a translation cue, or merely uses the signal as a rudimentary cue to self-motion. In the present study we tested between these two possibilities.

% Basic observations
We assessed self-motion perception during either body- and world-centered fixation at two different fixation depths. Our results show that self-motion was underestimated when comparing far and near fixation trials in the world-centered condition, which argues against a proper scaling of the eye movement signal. Fixation depth did not influence self-motion perception during body-centered fixation (where eye movements are virtually absent).

@@

In our previous experiment we compared body-fixed to world-fixed fixations at near (50 \si{\centi\metre}) distances only \cite{clemens2015a}. We compared the parameter, $\alpha$, found in that paper with the independently obtained parameter for the near condition, $\alpha_{50}$, from the present study. \figref{p4:fig6} shows how well our $\alpha_{50}$ parameter explains the data in our previous paper, the positive correlation between the actual PSEs and those predicted using the model in this paper ($\rho = 0.60$, $p = 0.06$) adds confidence to the parameter values presented here. The average difference between the values found here and those reported previously (see \tabref{p4:tab2}) is 12 \textpm 8 percent-points, indicating a variation of about 12\% on the contribution of the vestibular system versus that of the visual system between the present and our previous paper. While the variation might seem high, keep in mind that the two parameter values presented in this study are fitted on only four conditions, which do not overlap with the two conditions used to fit  parameter previously.

% Relation to the VOR
After showing that our present results in the nearby fixation condition are similar to those we found earlier, we go on and investigate to what extent the LVOR plays a role in the effects of eye movements on self-motion perception. Because the function of the LVOR is to keep the eyes stable in the world during linear translation, it also needs to scale with fixation depth \cite{paige1989, busettini1994,paige1998}. It is therefore possible that both the LVOR and self-motion perception have the same underlying same signal. Because of the visual fixation point, visual following mechanisms may even augment the LVOR compensation. If the oculomotor signal generated by the LVOR is the same signal that is used for self-motion perception, one would expect that the LVOR compensation at 50 and 200cm closely relate to the corresponding oculomotor weights in the present study (see \figref{p4:fig5} and \tabref{p4:tab2}). We derived the LVOR gains for 50 and 200 \si{\centi\metre} from Paige et al. \citeyear{1989} and computed their expected distance ratio, $d_{200} / d_{50}$. This ratio, 1.87, did not match either the ratio of the 6 participants who did not show any sign of scaling ($\frac{d_{200}}{d_{50}} = 1.07 \pm 0.16$) nor of the 2 participants that did show scaling ($\frac{d_{200}}{d_{50}} = 3.06 \pm 0.27$).

While we have shown that conscious perception of self-motion is influenced by eye movement, the same might not hold for actions based on self-motion. At the level of the vestibular system, it is known that perception of self-motion is influenced by the semicircular canals while the LVOR is not \cite{merfeld2005}, suggesting a more direct relation between the otolith signal and the LVOR. While it is unlikely that eye movements are used to drive the VOR because that would defeat the purpose of the eye movements themselves, we hypothesize that eye movements are also not used in other cases where latency is an important factor.

@@

In addition to the absence of scaling, is is possible that eye movement information is integrated in a statistically optimal fashion, that is taking the noise in the vestibular and oculomotor signals into account. While the vestibular signal and thus noise is constant for a given translation distance, the noise in the oculomotor estimate might depend on both the magnitude of the eye movement (i.e. signal dependent noise) as well as on the  fixation depth.

 If signal dependent noise would play a role, we would expect the large eye movements in the near world stationary fixation condition to be noisier than the small eye movement in the far world stationary condition. This would cause the nearby oculomotor estimate to be weighted less than than the far away one and would reduce the magnitude of our effect and, if the difference in noise levels is large enough, could even invert it. Because signal dependent noise would  weaken the observed effect, we discard it as a possible alternative.

 In addition to signal dependent noise, the noise levels in the oculomotor estimate could also depend on fixation depth. The retinal displacement of a world stationary fixation point decreases with fixation depth, making it less informative about the amount of self-motion. The noise level in the oculomotor estimate would therefore be higher for far away compared to nearby fixation points. For world stationary targets, this would predict an underestimation of self-motion while fixating far away compared to nearby, which is in line with our observations. However, it also predicts a similar effect for body stationary targets. As no such effects between the near and far body stationary fixation targets have been observed, we consider it an unlikely alternative explanation.

Could the lack of scaling be explained by how participants perceive the far fixation point? Because the difference between body- and world-fixed fixation points is reduced at far fixation distances, the lack of scaling could - in theory - be explained by participants incorrectly perceiving both the body- and world-fixed far fixation points as being body-fixed. We consider this an unlikely explanation, because the target displacement associated with a world-fixed target was between 0.3 and 8.5 degrees in our experiment, which is easily perceivable especially given that the target was foveated. This adds confidence to our claim that eye movements indeed influence self-motion perception, but with moderate to no scaling for fixation depth.

\subsection{Conclusion}
% Conclusion
In summary, fixation depth is not properly taken into account, suggesting that a relatively raw eye movement signal is used in self-motion perception. While efference copies of the eye movement signals or proprioceptive feedback could be directly responsible for the perceived self-motion, it cannot be ruled out that the signals that drive the eye movements are not causing the reported effects instead.

% Talk about whether perception and action employ different mechanisms?
% Check work by Merfeld
%
% Vestibular perception and action employ qualitatively different mechanisms I and II
% Merfeld, Park, Gianna-Pulin, Black, Wood, 2005
%

% -- %

% Self-motion perception; disambiguation
% Rotation perception; do not expect fixation distance to play a role

% Link to path reception during rotation, influence of instructions, depth range, and dot density:
% Li Li, William H. Warren Jr. doi:10.1016/j.visres/2004.03.008

% Experimental Brain Research doi:10.1007/s00221-009-1828-z 123
% Eye eccentricity modifies the perception of whole-body rotation
% Gaelle Quarck, Lena Lhuisset, Olivier Etart, Pierre Denise

>>>>

% Relation to previous work / Should rewrite this paragraph!
In our previous study, we demonstrated that oculomotor signals play a substantial role in the perception of translation, even in the absence of optic flow or any other visual stimulation \cite{clemens2015a}. Although the vestibular system provided the most significant contribution, oculomotor signals were shown to account for about 20\% of the overall percept. Because these experiments were performed with a single fixation depth, it was not clear whether the brain weighted the oculomotor signal in a depth-dependent manner when using it as a translation cue, or merely uses the signal as a rudimentary cue to self-motion. In the present study we tested between these two possibilities.

% Basic observations
We assessed translation perception during both body- and world-fixed fixation at two different fixation depths. Our results show that self-motion was underestimated when comparing far and near fixation trials in the world-fixed condition, which argues against a proper scaling of the eye movement signal. Fixation depth did not influence translation perception during body-fixed fixation (where eye movements are virtually absent).

@@

In our previous experiment we compared translation perception with body-fixed versus world-fixed fixations at near depth (50 \si{\centi\metre}) only \cite{clemens2015a}. \figref{p4:fig6} shows how well our $\alpha_{50}$ parameter explains the data in our previous paper. The highly positive correlation between the actual PSEs in the previous study and those predicted using the model of the present paper ($\rho = 0.60$, $p = 0.06$) adds confidence to the parameter values presented here. The average difference between the values found here and those reported previously (see \tabref{p4:tab2}) is 12 \textpm 8 percent-points, which is relatively small given the indpendent measurements.

% Relation to the VOR
The function of the LVOR is to keep the eyes stable in the world during linear translation \cite{paige1989,busettini1994,paige1998}. Because it also needs to scale with fixation depth \cite{angelaki2004}, it is possible that both the LVOR and self-motion perception have the same underlying same signal. Because of the visual fixation point, visual following mechanisms may even augment the LVOR compensation. If the oculomotor signal generated by the LVOR is used for self-motion perception, one would expect that the LVOR compensation at 50 and 200cm closely relate to the corresponding oculomotor weights in the present study (see \figref{p4:fig5} and \tabref{p4:tab2}). To further explore this, we derived the LVOR gains for 50 and 200 \si{\centi\metre} from Paige et al. \citeyear{paige1989} and computed their expected depth ratio, $d_{200} / d_{50}$. This ratio, 1.87, is in between the ratio of the 6 participants who did not show any sign of scaling ($\frac{d_{200}}{d_{50}} = 1.07 \pm 0.16$) and the 2 participants that did show scaling ($\frac{d_{200}}{d_{50}} = 3.06 \pm 0.27$).

@@

It is important to point out that while the vestibular signal and thus noise is constant for a given translation distance, the noise in the associated oculomotor estimate might not be, as the magnitude of the eye movement (i.e. signal-dependent noise) is modulated by fixation depth. If signal-dependent noise would play a role, nearby world-fixed fixations would cause larger eye movements with more noise compared to the far world-fixed fixations with smaller eye movements. The oculomotor based translation estimate would be weighted less for near versus far fixation, potentially explaining the partial compensation for fixation depth we have observed. In addition, the noise levels in the oculomotor estimate could also depend on fixation depth itself: the retinal displacement of a world stationary fixation point decreases with fixation depth, making it less informative about the amount of self-motion. The noise level in the oculomotor estimate would therefore be higher for far away compared to nearby fixation points. For world stationary targets, this would predict an underestimation of self-motion while fixating far away compared to nearby, which is in line with our observations. However, it also predicts a similar effect for body stationary targets. As no such effects between the near and far body stationary fixation targets have been observed, we consider it an unlikely alternative explanation.

Could the lack of scaling be explained by how participants perceive the distance of the fixation points? Because the difference between body- and world-fixed fixation points is reduced at far fixation distances, the lack of scaling could - in theory - be explained by participants incorrectly perceiving both the body- and world-fixed far fixation points as being body-fixed. We consider this an unlikely explanation, because the target displacement associated with a world-fixed target was between 0.3 and 8.5 degrees in our experiment, which is easily perceived. This adds confidence to our claim that eye movements influence self-motion perception, but with moderate to no scaling for fixation depth.

### 2015-03-24 src/paper4/p4_intro.tex
Updated paper 4

Our internal estimate of self-motion is used in a multitude of ways, among others, it keeps us from bumping into objects by providing accurate feedback on our movements and it allows us to track objects in the environment across intermittent self-motion. The vestibular system as well as optic flow provide essential information about self-motion \cite{gibson1955, benson1986, harris2000, israel1989, angelaki2005, carriot2013, chen2010}. However, the eye movements that typically occur to maintain visual acuity on important objects in the environment disturb the optic flow signal. Using the oculomotor signal, the brain accounts for these disturbances by internally separating optic flow in two components, one caused by self-motion and the other by eye movement  \cite{warren1988, royden1992, freeman1998, lappe1999}.

When the eyes track world-centered objects, their angular displacement is directly related to the size of the motion of the observer \cite{schwarz1989, paige1998, mchenry2000, medendorp2002}. Because  the majority of fixations are on world-stationary  objects, we recently proposed that these tracking eye movements could also be used as a self-motion cue, in addition to optic flow and vestibular signals. To test this hypothesis, we compared self-motion perception in the absence of full-field optic flow during passively induced whole-body translations \cite{clemens2015a}. Supporting the notion that eye movement can act as a self-motion cue, our results showed that self-motion is underestimated during body-centered fixations (in which the eyes remain stationary in their orbits) compared to fixations on world-stationary objects (in which the eyes must move to maintain fixation).

>>>>

An accurate internal estimate of self-motion is required to navigate effectively through a complex three-dimensional environment. The vestibular system as well as optic flow provide essential information about self-motion \cite{gibson1955, benson1986, harris2000, israel1989, angelaki2005, carriot2013, chen2010}. During navigation, however, the eye movements that typically occur to maintain visual acuity on important objects in the environment disturb the optic flow patterns. Using the oculomotor signal, the brain is able to account for these disturbances by internally separating optic flow in two components, one caused by self-motion and the other by eye movement \cite{warren1988, royden1992, freeman1998, lappe1999}.

When the eyes track world-centered objects, their angular displacement is directly related to the size of the motion of the observer \cite{schwarz1989, paige1998, mchenry2000, medendorp2002}. Because  the majority of fixations are on world-stationary  objects, we recently proposed that these tracking eye movements could also be used as a self-motion cue, in addition to optic flow and vestibular signals. To test this hypothesis, we compared self-motion perception in the absence of full-field optic flow during passively induced whole-body translations \cite{clemens2015a}. Our results showed that self-motion is underestimated during body-centered fixations (in which the eyes remain stationary in their orbits) compared to fixations on world-stationary objects (in which the eyes must move to maintain fixation).

### 2015-03-24 src/paper4/p4_methods.tex
Updated paper 4

Eight na\"ive participants (three male, five female), aged between 22 and 29 years, gave written informed consent to participate in the study. They were all free of any known vestibular or neurological disorder and had normal or corrected-to-normal visual acuity. Participants never received any feedback about their performance.  The experimental setup and methods used here are similar to those used in our previous paper on the influence of eye movement type on self-motion perception \cite{clemens2015a}. We only provide a brief summary here, and refer to our previous paper for further details.

@@

Participants were seated on a motorized linear sled with their body and head restrained such that the inter-aural axis aligned with the motion axis. The sled laterally translated participants following a minimum jerk profile of fixed duration (1 \si{\second}) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Auditory cues were suppressed using white noise presented through in-ear head-phones. Experiments were conducted in complete darkness except for visual fixation points, projected by body- or world-fixed laser pointers on a black bar, either 50 or 200 \si{\centi\metre} in front of the participant and at eye level. Eye movements were recorded at 500Hz using an EyeLink II (SR Research, Kanata, Canada) system. Eye position was calibrated before every session using 11 evenly spaced calibration points ranging from -22 to 22 degrees.

@@

The timing of a single trial is shown in \figref{p4:fig1}A. Every trial started with the onset of a central fixation point (i.e. aligned between the eyes) at 50 or 200\si{\centi\metre} for 0.5 \si{\second}. Subsequently, the first 1\si{\second} motion interval commenced; during this translation, the fixation point remained world stationary (world condition), or moved along with the participant (body condition).  Subsequently a 1.75 \si{\second} delay followed in which the sled was stationary and no  fixation light was shown. Next, a central fixation point reappeared at the depth (50 or 200\si{\centi\metre}) not used in the first interval. After 0.5 \si{\second}, the second 1 \si{\second} translation interval started, with the same fixation condition as in the first interval. After this second interval, the participant indicted whether the second displacement was perceived longer or shorter than the first by moving a 1-dimensional joystick away from (longer) or towards (shorter) the body. Top-view illustrations of example body-centered and world-centered trials are shown in \figref{p4:fig1} panels B and C respectively.

@@

% Should look at the 4 vs 16 in the next part, sounds confusing.
Across trials, we varied the order of the fixation depths and the order  of the reference and probe interval, resulting in four variations of the world and body conditions (see \tabref{p4:tab1}).

@@

The mean of the Gaussian, $\mu$, represents the point of subjective equality (PSE). The slope of the curve reflects the precision ($1/\sigma$) of reference-probe discrimination performance. Parameter $\lambda$, represents the lapse rate, accounts for stimulus-independent errors caused by subject lapses or mistakes and was restricted to small values ($\lambda < 0.06$). Fits were performed using the Psignifit toolbox \cite{wichmann2001,wichmann2001b}.

@@

By definition, at the PSE, the probe translation is perceived as equal in length to the 10 cm reference translation, $p_r = p_p$. By substituting both sides by the right hand side of \eqnref{p4:eq4}, we then obtain:

@@

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for every fixation depth (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth-dependent and a depth-independent scaling, we compute their ratio, $\frac{\alpha_{200}}{\alpha_{50}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{200}{50} = 4$, while in case of depth-independent scaling it is 1.

>>>>

Eight naive participants (three male, five female), aged between 22 and 29 years, gave written informed consent to participate in the study. They were all free of any known vestibular or neurological disorder and had normal or corrected-to-normal visual acuity. Participants never received any feedback about their performance.  The experimental setup and methods used here are similar to those used in our previous paper on the influence of eye movement type on self-motion perception \cite{clemens2015a}. We only provide a brief summary here, and refer to our previous paper for further details.

@@

Participants were seated on a motorized linear sled with their body and head restrained such that the inter-aural axis aligned with the motion axis. The sled laterally translated participants following a minimum jerk profile of fixed duration (1 \si{\second}) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Auditory cues were suppressed using white noise presented through in-ear head-phones. Experiments were conducted in complete darkness except for visual fixation points, projected by body- or world-fixed laser pointers on a black bar, either 50 or 200 \si{\centi\metre} in front of the participant and at eye level. Eye movements were recorded at 500Hz using an EyeLink II system (SR Research, Kanata, Canada). Eye position was calibrated before every session using 11 evenly spaced calibration points ranging from -22 to 22 degrees.

@@

The timing of a single trial is shown in \figref{p4:fig1}A. Every trial started with the onset of a central fixation point (i.e. aligned between the eyes), at a depth of 50 or 200\si{\centi\metre}, for 0.5 \si{\second}. Subsequently, the first 1\si{\second} motion interval commenced. During this translation, the fixation point either remained world stationary (world condition), or moved along with the participant (body condition).  Subsequently a 1.75 \si{\second} delay followed in which the sled was stationary and no  fixation light was shown. Next, a central fixation point reappeared at the other depth (50 or 200\si{\centi\metre}) than was used in the first interval. After 0.5 \si{\second}, the second 1 \si{\second} translation interval started, with the same fixation condition as in the first interval. After this second interval, the participant responded whether the second displacement was perceived longer or shorter than the first by moving a 1-dimensional joystick away from (longer) or towards (shorter) the body. Top-view illustrations of example body-centered and world-centered trials are shown in \figref{p4:fig1} panels B and C respectively.

@@

% Should look at the 4 vs 16 in the next part, sounds confusing.
Across trials, we varied the order of the fixation depths and the order  of the reference and probe interval, resulting in four variations of both the world and body condition (see \tabref{p4:tab1}).

@@

The mean of the Gaussian, $\mu$, represents the point of subjective equality (PSE). The slope of the curve reflects the precision ($1/\sigma$) of reference-probe discrimination performance. Parameter $\lambda$, representing the lapse rate, accounts for stimulus-independent errors caused by subject lapses or mistakes and was restricted to small values ($\lambda < 0.06$). Fits were performed using the Psignifit toolbox \cite{wichmann2001,wichmann2001b}.

@@

By definition, at the PSE, the probe translation is perceived as equal in length to the 10 cm reference translation, $p_r = p_p$. By substituting both sides by the right hand side of \eqnref{p4:eq4}, we obtain:

@@

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for each of the two fixation depths (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth-dependent and a depth-independent scaling, we compute their ratio, $\frac{\alpha_{200}}{\alpha_{50}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{200}{50} = 4$, while in case of depth-independent scaling it is 1.

### 2015-03-24 src/paper4/p4_results.tex
Updated paper 4

In a recent study we have shown that eye movement signals contribute to the perception of body translation, even in the absence of optic flow or a visual fixation point \cite{clemens2015a}. Because eye rotations must be scaled by target depth ($\varphi d = T$) to serve as an adequate translation cue, we tested self-motion perception for near (50 \si{\centi\metre}) and far (200 \si{\centi\metre}) fixations. Participants were presented with two subsequent translation movements \figref{p4:fig1} while they kept fixation on a world- or body-stationary target that was presented either nearby or far away. After the two intervals, they had to judge whether the second translation was longer or shorter than the first.

@@

    \caption{\panelref{A} Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference movements. \panelref{B} Normalized eye position for each participant (\textpm 95\% confidence interval) at the end of the translation interval for the near and far world fixed targets (purple and pink respectively) as well as the near and far body fixed fixation targets (brown and orange respectively). In addition, the average \textpm SE across all participants is shown. Zero indicates the eyes remained stationary relative to the body, and one indicates the eyes followed the near world fixed target perfectly.}
    \label{p4:fig2}
\end{figure}

We first investigated the ability of participants to fixate body and world stationary targets. \figref{p4:fig2}A depicts exemplar eye traces for the 10cm reference translation with nearby and far fixation points in both the body and world condition. Changes in gaze are largely absent in the body near and body far conditions (brown and orange traces respectively), as required. During the world conditions, the eye movements were large when fixating nearby targets and small when fixating far away ones (purple and pink traces respectively), which reflects the geometrical constraints.

We normalized the eye movement data by taking the average ratio between the measured eye excursion and the geometrically required displacement were the target world stationary. \figref{p4:fig2}B shows that these normalized eye displacements are about zero during body fixed fixations (brown and orange) and close to one in the world fixed fixations (purple and pink data points), for all participants. Our main question is whether these fixation depth dependent differences in eye movements are scaled by fixation depth in order to interpret them as linear self-motion cues.

@@

To investigate this question, \figref{p4:fig3} illustrates psychophysical data on self-motion perception of a single participant for the two-fixation depths in both the body (\figref{p4:fig3}A) and world condition (\figref{p4:fig3}B). Lighter and darker colors indicate which fixation depth was the reference translation (see figure legend). The influence of fixation depth is characterized by a shift of the psychometric functions relative to the 10 \si{\centi\metre} reference translation (i.e. the PSE). For example, the rightward shift of the pink curve in \figref{p4:fig3}B, representing the world-condition, means that with a far target a longer translation (\about15 \si{\centi\metre}) was required to be perceived equivalent to a 10 \si{\centi\metre} reference translation with nearby fixation. Likewise, the leftward shift of the purple curve indicates that a shorter translation with near fixation (\about6 \si{\centi\metre}) is required to be perceived the same as the 10 \si{\centi\metre} reference translation with far fixation. Together, these opposite biases suggest that translations are perceived shorter for fixations further away. The brown and orange curves in \figref{p4:fig3}A do not show such shifts, indicating that fixation depth (i.e. near versus far) has no effect in absence of eye movements (i.e. when fixating a body-fixed target during the translation).

Similar results were obtained for all participants, as shown by the individual PSEs (right column of \figref{p4:fig3}). Statistical significance of the effects of fixation depth was evaluated by comparing PSEs for the two fixation depths using a paired t-test. PSEs  differed significantly between the two fixation depths in the world condition, $t(7) = 5.42$, $p < 0.01$ (\figref{p4:fig3}C), but not in the body condition, $t(7) = -1.17$, $p = 0.28$ (\figref{p4:fig3}D), confirming the single subject results (\figref{p4:fig3}A, B). Thus, increasing fixation depth does not influence self-motion perception during body stationary fixations, but causes self-motion to be perceived as shorter during world stationary fixations.

@@

We used a simple linear model to quantify to what extent eye movements are scaled by fixation depth in order to serve as a linear self-motion cue (see \nameref{p4:sec:methods}). This model describes the perceived translation distance as a weighted average of a vestibular estimate, equal to the actual translation, and an oculomotor-based estimate. The latter estimate depends on the eye excursion which is possibly scaled by fixation depth. We used two weighting parameters, $\alpha_{50}$ and $\alpha_{200}$, one per fixation depth (see \tabref{p4:tab2} for best-fit values). Using these parameters we predicted the PSEs, i.e. $m_p$ in \eqnref{p4:eq5}, and plotted them against the actually observed PSEs in \figref{p4:fig4}. The positive correlation ($\rho = 0.xx$, $p < 0.01$)\footnote{DONT FORGET TO COMPUTE THIS; NEED ACCESS TO MATLAB THOUGH} between observed and predicted PSEs shows that our simple model does reasonably well in predicting perceptual performance.

>>>>

In a recent study we have shown that eye movement signals contribute to the perception of body translation, even in the absence of optic flow or a visual fixation point \cite{clemens2015a}. Because eye rotations must be scaled by target depth ($\varphi d = T$) to serve as an adequate translation cue, we tested self-motion perception for near (50 \si{\centi\metre}) and far (200 \si{\centi\metre}) fixations. Participants were presented with two subsequent translations \figref{p4:fig1} while they kept fixation on a world- or body-stationary target that was presented either nearby or far away. After the two translation intervals, they had to judge whether the second translation was longer or shorter than the first.

@@

    \caption{\panelref{A} Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference displacements. \panelref{B} Normalized eye position for each participant (\textpm 95\% confidence interval) at the end of the translation interval for the near and far world fixed targets (purple and pink respectively) as well as the near and far body fixed fixation targets (brown and orange respectively). In addition, the average \textpm SE across all participants is shown. Zero indicates the eyes remained stationary relative to the body, and one indicates the eyes followed the near world fixed target perfectly.}
    \label{p4:fig2}
\end{figure}

We first investigated the ability of participants to fixate body and world stationary targets. \figref{p4:fig2}A depicts exemplar eye traces for the 10cm reference translation with nearby and far fixation points in both the body and world condition. Changes in gaze are largely absent in the body near and body far conditions (brown and orange traces respectively), as required. During the world conditions, the eye excursions were large when fixating nearby targets and small when fixating far away ones (purple and pink traces respectively), which reflects the geometrical constraints.

We normalized the eye movement data by taking the average ratio between the measured eye excursion and the geometrically required eye displacement were the target world stationary. \figref{p4:fig2}B shows that these normalized eye displacements are about zero during body fixed fixations (brown and orange) and close to one in the world fixed fixations (purple and pink data points), for all participants. The question is whether these eye movements are scaled by fixation depth in order to interpret them as linear self-motion cues.

@@

To answer this question, \figref{p4:fig3} illustrates psychophysical data on self-motion perception of a single participant for the two-fixation depths in both the body (\figref{p4:fig3}A) and world condition (\figref{p4:fig3}B). Lighter and darker colors indicate which fixation depth was the reference translation (see figure legend). The influence of fixation depth is characterized by a shift of the psychometric functions relative to the 10 \si{\centi\metre} reference translation (i.e. the PSE). For example, the rightward shift of the pink curve in \figref{p4:fig3}B, representing the world-condition, means that with a far target a longer translation (\about15 \si{\centi\metre}) was required to be perceived equivalent to a 10 \si{\centi\metre} reference translation with nearby fixation. Likewise, the leftward shift of the purple curve indicates that a shorter translation with near fixation (\about6 \si{\centi\metre}) is required to be perceived the same as the 10 \si{\centi\metre} reference translation with far fixation. Together, these opposite biases suggest that translations are perceived shorter for fixations further away. The brown and orange curves in \figref{p4:fig3}A do not show such shifts, indicating that fixation depth (i.e. near versus far) has no effect in absence of eye movements (i.e. when fixating a body-fixed target during the translation).

Similar results were obtained for all participants, as shown by the individual PSEs (right column of \figref{p4:fig3}). Statistical significance of the effects of fixation depth was evaluated by comparing PSEs for the two fixation depths using a paired t-test. PSEs  differed significantly between the two fixation depths in the world condition, $t(7) = 5.42$, $p < 0.01$ (\figref{p4:fig3}C), but not in the body condition, $t(7) = -1.17$, $p = 0.28$ (\figref{p4:fig3}D), confirming the single subject results (\figref{p4:fig3}A, B). Thus, increasing fixation depth does not influence self-motion perception during body-fixed fixations, but causes self-motion to be perceived as shorter during world-fixed fixations.

@@

We used a simple linear model to quantify to what extent eye movements are scaled by fixation depth in order to serve as a linear self-motion cue (see \nameref{p4:sec:methods}). This model describes the perceived translation as a weighted average of a vestibular estimate, equal to the actual translation, and an oculomotor-based estimate. The latter estimate depends on the eye excursion which is possibly scaled by fixation depth. We used two weighting parameters, $\alpha_{50}$ and $\alpha_{200}$, one per fixation depth (see \tabref{p4:tab2} for best-fit values). Using these parameters we predicted the PSEs, i.e. $m_p$ in \eqnref{p4:eq5}, and plotted them against the actually observed PSEs in \figref{p4:fig4}. The positive correlation ($\rho = 0.xx$, $p < 0.01$)\footnote{DONT FORGET TO COMPUTE THIS; NEED ACCESS TO MATLAB THOUGH} between observed and predicted PSEs shows that our simple model does reasonably well in predicting perceptual performance.
